GEE models

### 2017-10-02 doc/manuscript.Rmd
naming format change (acknow), duality of interest, and guarantor

The authors thank Jan Neuman, Paula Van Nostrand, Stella Kink, and Annette
Barnie of the Leadership Sinai Centre for Diabetes, Mount Sinai Hospital,
Toronto, Canada and Sheila Porter and Mauricio Marin of the Centre for Studies
in Family Medicine, University of Western Ontario, London, Canada for their 
expert technical assistance and dedication in their work for PROMISE.

@@

This study was supported by grants from the Canadian Diabetes Association (CDA),
the Canadian Institutes for Health Research, and the University of
Toronto Banting and Best Diabetes Centre; LWJ is supported by a CDA
Doctoral Student Research Award; RR is supported by a Heart and Stroke
Foundation of Ontario Mid-Career Investigator Award; SBH holds the CDA Chair in
National Diabetes Management and the Ian McWhinney Chair of Family Medicine
Studies at the University of Western Ontario; RBP holds a Tier II Canada
Research Chair in Brain Lipid Metabolism; AJH holds a Tier II Canada Research
Chair in Diabetes Epidemiology.

@@

The authors report no potential conflicts of interest relevant to this study.

@@

The authors had the following responsibility: LWJ conducted research, analyzed
data, and wrote the paper; RR, ZL, and SBH designed research, conducted
research, and provided essential materials (infrastructure and clinical
resources); RR, SBH, RPB, and AG provided intellectual feedback on the
paper; RPB conducted research, provided essential reagents and materials; AJH
designed research, assisted with interpretation, and provided intellectual
feedback on all versions of the paper; LWJ and AJH had primary responsibility
for final content. All authors read and approved the final manuscript.

>>>>

The authors thank J Neuman, PV Nostrand, S Kink, and A Barnie (all of the
Leadership Sinai Centre for Diabetes, Mount Sinai Hospital, Canada) and
S Porter and M Marin (both of the Centre for Studies in Family Medicine,
University of Western Ontario, Canada) for their expert technical
assistance and dedication in their work for PROMISE.

@@

This study was supported by grants from the Canadian Diabetes Association (CDA),
the Canadian Institutes for Health Research, and the University of Toronto
Banting and Best Diabetes Centre; LWJ was supported by a CDA Doctoral Student
Research Award; RR was supported by a Heart and Stroke Foundation of Ontario
Mid-Career Investigator Award; SBH holds the CDA Chair in National Diabetes
Management and the Ian McWhinney Chair of Family Medicine Studies at the
University of Western Ontario; RPB holds a Tier II Canada Research Chair in
Brain Lipid Metabolism; AJH holds a Tier II Canada Research Chair in Diabetes
Epidemiology.

@@

The authors declare that there is no duality of interest associated with this
manuscript.

@@

The authors had the following responsibility: LWJ conducted research, analyzed
data, and wrote the paper; RR, ZL, and SBH designed research, conducted
research, and provided essential materials (infrastructure and clinical
resources); RR, SBH, RPB, and AG provided intellectual feedback on the
paper; RPB conducted research, provided essential reagents and materials; AJH
designed research, assisted with interpretation, and provided intellectual
feedback on all versions of the paper; LWJ and AJH had primary responsibility
for final content and are the guarantors of this work. All authors read and
approved the final manuscript.
